**Preprinting Microbiology**

### 2017-02-23 submission/Schloss_PrePrints_mBio_2017.Rmd
Update deposition date
minor typos, PrePubMed, ScienceOpen

***Background.*** Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public. A preprint is an interim research product, such as an unpublished manuscript, made publicly available before going through an official peer-review process [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016]. Authors can post their manuscript to a preprint server for others to read, share, and comment. Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues [@Nature1966]. While the biological community's commitment to preprints waned, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011]. For some physicists and mathematicians, posting a preprint to *arXiv* followed by submission to a peer-reviewed journal has become a standard publication pathway. Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists. Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012]. Considering the broadening adoption of preprints among microbiologists, I sought to explore the specific uses of and concerns regarding preprints.

***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013]. Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded. There are several important differences between the two options. First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory. This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations. Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse. This can be relevant for authors hoping to submit their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g. *Proceedings of the National Academy of Sciences*). The flexibility of the *bioRxiv* licensing empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research results however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option. A cosmetic, but still relevant difference between the two is the layout and feel of the two websites. Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints. With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*. It is only possible to transfer a *PeerJ Preprint* for submission to *PeerJ*. In many ways, preprint servers have taken on the feel of a journal. As adoption of this approach expands, it is likely that the features of these sites will continue to improve. It is also likely that interfaces from third-parties will improve. For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not. There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications. As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted. It is therefore essential to balance the requirements placed on authors for features associated with preprints with the current desirable efficiency of the preprint format.

@@

First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies. Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of January 2017 the number of Zika virus-related publications was over 1,700. During the recent outbreak, more than 110 Zika virus-related preprints have been posted at *bioRxiv*. Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus. In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly. Over the last several years there have also been rapid advances in DNA sequencing technologies have fundamentally changed how microbial science is performed. One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 90 preprints describing new MinIon-based methods and results to preprint servers. For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.

@@

Measuring the impact and significance of scientific research is notoriously difficult. Using several metrics I sought to quantify the effect that broadly defined microbiology-affiliated preprints have had on the work of others. Using the download statistics associated with each preprint, I found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively. These values represent two aspects of posting a preprint. First, they reflect the number of times people were able to access science before it was published. Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall. To obtain a measure of a preprint's ability to garner attention and engage the public, I obtained the Altmetric Attention Score for each preprint (**Figure 1B**). The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, traditional media, Wikipedia, policy documents, and other sources [@Altmetric]. A higher score indicates that a preprint received more attention. Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). For comparison, the median Altmetric Attention Score for articles published in *mBio* published since 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(round(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *bioRxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`. A more traditional and controversial metric of impact has been the number of citations an article receives. I obtained the number of citations for the published versions of manuscripts that were initially posted as preprints. To allow for a comparison to traditional journals, I considered the citations for preprints published in 2014 and 2015 as aggregated by Web of Science (**Figure 1C**). Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`). For comparison, for the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`). Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community.

***Preprints from an author's perspective.*** Posting research as a preprint gives an author great control over when their work is made public. Under the traditional peer-review model, an author may need to submit and revise their work multiple times to several journals over a long period before it is finally published. In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process. A first example illustrates the utility of preprints for improving access to research and the quality of its reporting. In 2014, my research group posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform [@Schloss2015]. At the same time, they submitted the manuscript for review at *PeerJ*. While the manuscript was under review, they received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry. Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from the academic scientist and Pacific Biosciences. It was eventually published by *PeerJ* [@Schloss2016a; @Schloss2016b]. Since 2015, we have continued to post manuscripts as preprints at the same time as we have submitted manuscripts. Although the feedback to other manuscripts has not been as helpful as our initial experience, we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b]. As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **February XX, 2017**. I then solicited feedback on the manuscript using social media. Two weeks later, I incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*. During that time, the abstract was read **XXXX** times and the PDF was accessed **XXXX** times. This process engaged **XXXX** commenters on *bioRxiv*, **XXXX** people on Twitter, **XXXX** on Facebook, and **XXXX** via email. I received useful feedback from **XXX** people. Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had I foregone the posting of a preprint. Although there are concerns regarding the quality of the science posted to a preprint server, I contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.

***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals will have in disseminating research if there is broad adoption of preprints. Edited peer-reviewed journals offer and will continue to offer significant added value to a publication. A scholarly publishing ecosystem in which preprints coexist with journals will allow authors to gain value from the immediate communication of their work associated with preprints and also benefit from the peer-reviewed, professionally edited publication that publishers can provide.
The professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals. An alternative perspective is that preprints will eventually replace traditional journals. Certainly, this is a radical perspective, but it does serve to motivate publishers to capture the innovation opportunities offered by preprints. By adopting preprint-friendly policies, journals can create an attractive environment for authors. As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals. An example is offered by the ASM, which earlier this year launched a new venture from *mSphere*. mSphereDirect is a publication track of the journal that capitalizes on the opportunity offered to couple preprints with rigorous peer-review. mSphereDirect. actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016]. ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication). In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016]. These are policies that empower authors and make specific journals more attractive. Other practices have great potential to improve the reputation of journals. As measured above, preprints are able to garner attention on par with papers published in highly selective microbiology journals. Thus, it is in a journal's best interest to recruit these preprints to their journals. Several journals including *PLOS Genetics* and *Genome Biology* have publicly stated that they scout preprints for this purpose [@Vence2017; @Barsh2016]. Preprints can also be viewed as a lost opportunity to journals. A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal. Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.

>>>>

***Background.*** Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public. A preprint is an interim research product, such as an unpublished manuscript, made publicly available before going through an official peer-review process [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016]. Authors can post their manuscript to a preprint server for others to read, share, and comment. Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues [@Nature1966]. While the biological community's commitment to preprints waned, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011]. For some physicists and mathematicians, posting a preprint to *arXiv* optionally followed by submission to a peer-reviewed journal has become a standard publication pathway. Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists. Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012]. Considering the broadening adoption of preprints among microbiologists, I sought to explore the specific uses of and concerns regarding preprints.

***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013]. Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded. There are several important differences between the two options. First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory. This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations. Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse. This can be relevant for authors hoping to submit their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g. *Proceedings of the National Academy of Sciences*). The flexibility of the *bioRxiv* licensing empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research results however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option. A cosmetic, but still relevant difference between the two is the layout and feel of the two websites. Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints. With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*. It is only possible to transfer a *PeerJ Preprint* for submission to *PeerJ*. In many ways, preprint servers have taken on the feel of a journal. As adoption of this approach expands, it is likely that the features of these sites will continue to improve. It is also likely that interfaces from third-parties will improve. For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not. For this reason an independent PrePubMed indexing and search engine was developed (<http://www.prepubmed.org/>). Additionally, the for-profit publishing network ScienceOpen (<https://www.scienceopen.com/>) indexes *arXiv* preprints and opens up a discussion channel, which is not available on the *arXiv* website. There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications. As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted. It is therefore essential to balance the requirements placed on authors for features associated with preprints with the current desirable efficiency of the preprint format.

@@

First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies. Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of January 2017 the number of Zika virus-related publications was over 1,700. During the recent outbreak, more than 110 Zika virus-related preprints have been posted at *bioRxiv*. Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus. In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly. Over the last several years there have also been rapid advances in DNA sequencing technologies that have fundamentally changed how microbial science is performed. One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 90 preprints describing new MinIon-based methods and results to preprint servers. For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.

@@

Measuring the impact and significance of scientific research is notoriously difficult. Using several metrics I sought to quantify the effect that broadly defined microbiology-affiliated preprints have had on the work of others. Using the download statistics associated with each preprint, I found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively. These values represent two aspects of posting a preprint. First, they reflect the number of times people were able to access science before it was published. Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall. To obtain a measure of a preprint's ability to garner attention and engage the public, I obtained the Altmetric Attention Score for each preprint (**Figure 1B**). The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, traditional media, Wikipedia, policy documents, and other sources [@Altmetric]. A higher score indicates that a preprint received more attention. Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). For comparison, the median Altmetric Attention Score for articles published in *mBio* published since 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(round(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *bioRxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`). A more traditional and controversial metric of impact has been the number of citations an article receives. I obtained the number of citations for the published versions of manuscripts that were initially posted as preprints. To allow for a comparison to traditional journals, I considered the citations for preprints published in 2014 and 2015 as aggregated by Web of Science (**Figure 1C**). Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`). For comparison, for the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`). Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community.

***Preprints from an author's perspective.*** Posting research as a preprint gives an author great control over when their work is made public. Under the traditional peer-review model, an author may need to submit and revise their work multiple times to several journals over a long period before it is finally published. In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process. A first example illustrates the utility of preprints for improving access to research and the quality of its reporting. In 2014, my research group posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform [@Schloss2015]. At the same time, they submitted the manuscript for review at *PeerJ*. While the manuscript was under review, they received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry. Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from the academic scientist and Pacific Biosciences. It was eventually published by *PeerJ* [@Schloss2016a; @Schloss2016b]. Since 2015, we have continued to post manuscripts as preprints at the same time as we have submitted manuscripts. Although the feedback to other manuscripts has not been as helpful as our initial experience, we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b]. As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **February 22, 2017**. I then solicited feedback on the manuscript using social media. Two weeks later, I incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*. During that time, the abstract was read **XXXX** times and the PDF was accessed **XXXX** times. This process engaged **XXXX** commenters on *bioRxiv*, **XXXX** people on Twitter, **XXXX** on Facebook, and **XXXX** via email. I received useful feedback from **XXX** people. Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had I foregone the posting of a preprint. Although there are concerns regarding the quality of the science posted to a preprint server, I contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.

***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals will have in disseminating research if there is broad adoption of preprints. Edited peer-reviewed journals offer and will continue to offer significant added value to a publication. A scholarly publishing ecosystem in which preprints coexist with journals will allow authors to gain value from the immediate communication of their work associated with preprints and also benefit from the peer-reviewed, professionally edited publication that publishers can provide.
The professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals. An alternative perspective is that preprints will eventually replace traditional journals. Certainly, this is a radical perspective, but it does serve to motivate publishers to capture the innovation opportunities offered by preprints. By adopting preprint-friendly policies, journals can create an attractive environment for authors. As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals. An example is offered by the ASM, which earlier this year launched a new venture from *mSphere*. mSphereDirect is a publication track of the journal that capitalizes on the opportunity offered to couple preprints with rigorous peer-review. mSphereDirect actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016]. ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication). In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016]. These are policies that empower authors and make specific journals more attractive. Other practices have great potential to improve the reputation of journals. As measured above, preprints are able to garner attention on par with papers published in highly selective microbiology journals. Thus, it is in a journal's best interest to recruit these preprints to their journals. Several journals including *PLOS Genetics* and *Genome Biology* have publicly stated that they scout preprints for this purpose [@Vence2017; @Barsh2016]. Preprints can also be viewed as a lost opportunity to journals. A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal. Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.
